---
output: 
    html_document:
        theme: readable
params:
    dist: "27661590000000"
---

<a href="https://github.com/dobrowski/LCAPmetrics" class="github-corner" aria-label="View source on GitHub"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#151513; color:#fff; position: absolute; top: 0; border: 0; right: 0;" aria-hidden="true"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(here)
library(rmarkdown)
library(knitr)
library(tidyverse)
library(glue)
# library(DT)
library(gt)


options(scipen=999)

dist <- params$dist

indicators <- read_rds("indicators.rds")
metrics <- read_rds("metrics.rds")
dashboard_mry <- read_rds("dashboard_mry.rds")
lcap.reds <- read_rds("lcap_reds.rds")
lrebg <- read_rds("lrebg.rds")
lcap.reds.into.2024 <- read_rds("lcap_reds_into_2024.rds")
lcap.reds.pivot <- read_rds("lcap_reds_pivot.rds")
csi_mry <- read_rds("csi_mry.rds")
em_mry <- read_rds("em_mry.rds")
undup.count <- read_rds("undup.rds")
el.count <- read_rds("el.rds")
ltel.count <- read_rds("ltel.rds")
dash.mry.da <- read_rds("dash_mry_da.rds")
req.goals.student <- read_rds("req_goals_student.rds")
mid.year.resources <- read_rds("mid_year_resources.rds")


colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
      x)
  } else x
}


ind_dist <- indicators %>%
    filter(cds == dist) 

metrics_dist <- ind_dist %>% 
    t() %>%
    as.data.frame() %>%
    transmute(metrics = row.names(.),
           rate = as.character(.$V1)
           )

joinder <- left_join(metrics, metrics_dist) %>%
    mutate(sentence = if_else(is.na(rate),
                              colorize( glue("<p style='background-color:wheat;'>The {description} is unavailable in public data sets.  It can be located in {source}. {notes} </p>"),"gray35"),
                              colorize( glue("<p style='background-color:sandybrown;'> The {description} for {year} is ***{rate}*** based on data from {website}. {notes} </p>"
                                             ), "black")
                              )
    )




charter.school.codes <- c(
"27102720112177" , # Monterey Bay Ch…
"27102720116491" , # Open Door Chart…
"27102720124297" , # Bay View Academy
"27102722730232" , # Monterey County…
"27102726119663" , # Oasis Charter P…
"27660922730240" , # Learning for Li…
"27751500118349" , # Big Sur Charter 
"27660926118962"  # International S…
    ) 


# write_csv(joinder  ,here("output",paste0(metrics_dist[18,2]," data.csv" ) ))

```



---
title: `r metrics_dist[4,2]` 2024-25 Student Success Portal
---


## Report Purpose

The purpose of this project is to provide all districts with as many of the required LCAP metrics as possible. It draws on public datasources including the California Dashboard and CDE's downloadable data files (https://www.cde.ca.gov/ds/sd/sd/). It is meant to save time looking things up, and is completely optional to use. Items with grey text and light brown background do not have publicly available data for your LEA, whereas items in black and the darker brown do have data available to present. Your LEA may not have data available because that indicator does not apply such as elementary districts and graduation rate. 

Please note that the most recently available data is used, with a preference for the California Dashboard.  Additional data represented comes from DataQuest.  Most data reflect the 2023-24 school year, but in some case may represent the current school year or prior years. MCOE and CDE also encourage you to use current local data from your School Information System or other sources.  

Please do not use Safari.  Important Data will only appear with Chrome or Firefox. 


-----------

## Mid-Year Update Resources


```{r midyear, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

mid.year.dist <- mid.year.resources %>%
    mutate(cds = as.character(cds)) %>%
        filter(cds == dist) 


 dashboard_slides_address <- mid.year.dist$dashboard.slides
 
midyear_slides_address <- mid.year.dist$midyear.slides
 
tracker_sheets_address <- mid.year.dist$tracker.sheets


cat("MCOE has created multiple Mid-Year Update resources that LEAs have the option of using.  These include a [Actions Tracking Sheet, a Metrics Tracking Sheet,](",tracker_sheets_address,") [Dashboard Summary Slide Deck](",dashboard_slides_address,") and [Sample Board Presentation Slide Deck](",midyear_slides_address,"). In addition the data on this webpage can be used to update and inform the board.")
```



-----------

## Plan Summary

These data points need to be included in the Plan Summary section, along with steps being taken to address them.  Additional identified needs from local data or educational partner processes can also be included. 

```{r needs, echo=FALSE, include=FALSE}

ind_long_names <- tibble(indicator = c("cci","elpi","ela", "math", "grad", "chronic", "susp"),
                         long = c("College and Career", "English Language Progress Indicator", "English Language Arts CAASPP scores", "Math CAASPP scores", "Graduation Rate", "Chronic Absenteeism", "Suspensions"))

studentgroups <- tibble(name = c("ALL", "AA", "AI", "AS", "FI", "HI", "PI", "WH", "MR", "EL", "ELO", "EO", "SED", "SWD", "FOS", "HOM"),
                        descriptive = c(
                            "All Students",
                            "Black/African American",
                            "American Indian or Alaska Native",
                            "Asian",
                            "Filipino",
                            "Hispanic",
                            "Pacific Islander",
                            "White",
                            "Multiple Races/Two or More",
                            "English Learner",
                            "English Learner Only",
                            "English Only",
                            "Socioeconomically Disadvantaged",
                            "Students with Disabilities",
                            "Foster",
                            "Homeless")
)



lea.need <- dashboard_mry %>% 
    filter(cds == dist,
           studentgroup == "ALL",
           statuslevel == 1
#           color %in% c(1,2)
    ) %>%
    select(indicator) %>%
    left_join(ind_long_names)


lea.sub.low <- dashboard_mry %>%
    filter(cds == dist) %>%
#    select(cds,ind, studentgroup, color) %>%
    select(indicator, studentgroup, statuslevel) %>%
    filter(statuslevel >0) %>%
    group_by(indicator) %>%
    pivot_wider(names_from = studentgroup, values_from = statuslevel) %>%
    pivot_longer(cols = -c(ALL, indicator) ) %>%
    mutate(diff = ALL - value) %>%
    filter(!is.na(value) & value != 0) %>%
    filter(diff >= 2) %>%
    left_join(ind_long_names) %>%
    left_join(studentgroups) %>%
    mutate(phrases = glue("{descriptive} youth for {long}"))




undup.mets <- dashboard_mry %>%
    filter(cds == dist,
           !is.na(indicator),
           studentgroup %in% c("EL","FOS","SED")) %>%
    select(indicator, studentgroup, currstatus)  %>%
    mutate(indicator = tolower(indicator)) %>%
    mutate(indicator = if_else(indicator == "chro", "chronic", indicator)) %>%
    left_join(ind_long_names) %>%
    left_join(studentgroups, by = c("studentgroup" = "name")) %>%
    select(long, descriptive, currstatus)





# Blocked out for this year since not relevant

redorange <- if ( length( lea.need$long) > 0 ) combine_words( lea.need$long) else
                       "No indicators"

student.need <- if ( length( lea.sub.low$phrases) > 0 ) combine_words( lea.sub.low$phrases) else
                       "No student groups"


### DA ----

da.dist <- dash.mry.da %>%
    filter(cds == dist,
           !is.na(indicator2)) %>%
    select(studentgroup.long,indicator2) %>%
    arrange(studentgroup.long,indicator2)



# 
# ### Indicators which are Lowest Status overall 
# 
# `r redorange` were the lowest status on the dashboard for ALL students overall.
# 
# 
# ### Student groups whose performance level was two or more levels below students overall
# 
# `r student.need` were two or more performance levels below ALL students in the district.




```


### General Information

For example, information about an LEA in terms of geography, enrollment, employment, the number and size of specific schools, recent community challenges, and other such information the LEA may wish to include can enable a reader to more fully understand the LEA’s LCAP. 

As part of this response, identify all schools within the LEA receiving Equity Multiplier funding. 



------

### Reflections: Lowest Performing

As part of this response, the LEA must identify all schools, student groups and student groups at schools which were at the lowest performance level on the 2023 Dashboard. These student groups will remain unchanged during the three-year LCAP cycle and the most recent data is added to the table. 


<details>

<summary>[**Click here to display table**]{style="color:green;"}</summary>

```{r reds, echo=FALSE, include=TRUE, results = 'asis'}


### Dashboard Reds -----

dist.name <- metrics_dist[4,2]

lcap.reds.into.2024 <- lcap.reds.into.2024 %>%
    filter(districtname == dist.name,
           
           ) %>% 
     select(indicator, studentgroup.long, schoolname, status2023, status2024, lrebg) %>%
    arrange(indicator, studentgroup.long, schoolname)


# gt::gt(lcap.reds) |>
#         tab_header(title = "Red Student Groups and Indicators on Dashboard") |>
#       tab_source_note(source_note = "Source: https://www.caschooldashboard.org/" ) |>
#   cols_label(
#     studentgroup.long = html("Student Group"),
#     indicator = html("Indicator"),
#         schoolname = html("School Name"),
#     currstatus = html("2023 Status")
# 
#   )



DT::datatable(lcap.reds.into.2024,
              rownames = FALSE,
              colnames = c("Indicator","Student Group", "School Name", "2023 Status","2024 Status","Also LREBG Identified" ),
              options = list(pageLength = 10)
              )



```


</details>



------

### Learning Recovering Emergency Block Grant (LREBG)

As part of the LREBG, all LEAs with unexpended funds needs to conduct a needs assessment.  As part of the needs assessment, all student groups in the Low or Very Low STATUS (not color) according to the 5x5 (https://www.cde.ca.gov/ta/ac/cm/fivebyfivecolortables23.asp) need to be identified.  The following table identifies those schools and student groups for this part of the needs assessment.  Individual students will also need to be identified as per the Needs Assessment instructions.  


<details>

<summary>[**Click here to display table**]{style="color:pink;"}</summary>

```{r lrebg, echo=FALSE, include=TRUE, results = 'asis'}


### Dashboard Reds -----

dist.name <- metrics_dist[4,2]

lrebg.disp <- lrebg %>%
    filter(districtname == dist.name,
           
           ) %>% 
     select(indicator, studentgroup.long, schoolname, statuslevel, currstatus, changelevel ,change) %>%
    arrange(indicator, studentgroup.long, schoolname)


# gt::gt(lcap.reds) |>
#         tab_header(title = "Red Student Groups and Indicators on Dashboard") |>
#       tab_source_note(source_note = "Source: https://www.caschooldashboard.org/" ) |>
#   cols_label(
#     studentgroup.long = html("Student Group"),
#     indicator = html("Indicator"),
#         schoolname = html("School Name"),
#     currstatus = html("2023 Status")
# 
#   )



DT::datatable(lrebg.disp,
              rownames = FALSE,
              colnames = c("Indicator","Student Group", "School Name", "Status Level","2024 Status", "Change Level", "2024 Change" ),
              options = list(pageLength = 10)
              )



```


</details>




------

### Reflections: Technical Assistance 

Districts that are eligible for Differentiate Assistance need to identify the reason(s) the LEA is eligible and provide a summary of the work underway as part of receiving technical assistance. 

```{r da-table, echo=FALSE, message=FALSE, include=FALSE}

# da.need <- if ( length( da.dist$studentgroup.long) > 0 ) {datatable(da.dist,
#           colnames = c("Student Group", "Indicator"),
#           caption = "Student Groups Qualifying for DA on 2023 Dashboard",
#           rownames = FALSE,
#           
#           options = list(pageLength = 20,
#                          lengthChange = FALSE,
#                          searching = FALSE,
#                          dom = 't'))} else
#                        "The District is not eligible for DA"

da.need <- if ( length( da.dist$studentgroup.long) > 0 ) {
    gt(da.dist) |>
        tab_header(title = "DA Eligible Student Groups and Indicators") |>
      tab_source_note(source_note = "Source: https://www.cde.ca.gov/fg/aa/lc/" ) |>
  cols_label(
    studentgroup.long = html("Student Group"),
    indicator2 = html("Indicator"),
  )
    
    } else "The District is not eligible for technical assistance"


# da.need2 <- if ( length( da.dist$studentgroup.long) > 0 ) print("You can find additional data at https://da-monterey.netlify.app/") else print("")

if ( length( da.dist$studentgroup.long) > 0 ) {
    da.need
    } else print("The District is not eligible for technical assistance")

```


`r da.need`


-----------

### Comprehensive Support and Improvement 

For CSI identified schools, it is required to address the three CSI prompts in the LCAP template. 


```{r csi, echo=FALSE, include=FALSE}


csi <- csi_mry %>% 
    filter(cds == dist) 

csi.words <- if ( length( csi$schoolname) > 0 ) paste0(combine_words( csi$schoolname), " have been identified as CSI schools.") else paste0("There are no schools in the district identified for CSI and the section can be skipped by entering '", metrics_dist[4,2],  " does not have any schools identified as CSI'.")

```


`r csi.words`



-----------

## Engaging Educational Partners 

Consistent with statute, engagement should support comprehensive strategic planning, particularly to address and reduce disparities in opportunities and outcomes.  The following Educational Partners must be consulted:  



```{r ed-partners, echo=FALSE, include=FALSE}


ed.partner.words <- if ( dist %in% charter.school.codes ) " + Teachers
+ Principals
+ Administrators
+ Other school personnel
+ Parents
+ Parent Advisory Committee
+ ELAC
+ DELAC
+ Special Education 
+ Students" else "+ Teachers
+ Principals
+ Administrators
+ Other school personnel
+ Local bargaining units of the LEA
+ Parents
+ Parent Advisory Committee
+ ELAC
+ DELAC
+ Special Education 
+ Students"

```


`r ed.partner.words`

A school district or COE receiving Equity Multiplier funds must also consult with educational partners at schools generating Equity Multiplier funds in the development of the LCAP, specifically, in the development of the required focus goal for each applicable school. 


## Goals and Actions


### Required Goals: Equity Multiplier Schools 


```{r em, echo=FALSE, include=FALSE}


em <- em_mry %>% 
    filter(cds == dist) 

em.words <- if ( length( em$school_name) > 0 ) paste0(combine_words( em$school_name), " have been identified as Equity Multiplier schools. 
                                                      
It is required to establish a Focus Goal addressing the qualifications for the equity multiplier school. It is also necessary to talk to your educational partners about the use of the funds. It is also required to identify all schools within the LEA receiving Equity multiplier funding in the [General Information] Section.

Please see https://www.cde.ca.gov/fg/aa/lc/equitymultiplier.asp for additional details.") else paste0("There are no schools in the district identified as Equity Multiplier schools.")

```


`r em.words`


-------

### Required Actions: Reds on the Dashboard 

LEAs are required to include actions for every Red indicator on their Dashboard for student groups, schools, or student groups at schools. 

Note these are listed above in the [Reflections: Lowest Performing] section. 



-------

### Required Actions: Differentiated Assistance

LEAs eligible for Differentiated Assistance must include specific actions related to implementation of work underway. 

Note these are listed above in the Technical Assistance section. 


------

### Required Actions: English Learners and Long-Term English Learners


```{r el, echo=FALSE, include=FALSE}


# EL 

el.lang <- el.count %>% 
    filter(cds == dist) 


el.words <- glue( "The most recent percentage of EL students from https://www.cde.ca.gov/ds/sd/sd/filescupc.asp was **{ scales::percent( el.lang$el.perc , accuracy = .1 ) }**.  The total count of EL students was **{ el.lang$el.count }**.  ") 

el.words2 <- if ( el.lang$el.perc >= .15 | el.lang$el.count >=50 ) " Your district is required to have a DELAC, Language acquistion programs, and professional development for teachers." else " Your district is NOT required to have a DELAC."

# LTEL

ltel.lang <- ltel.count %>% 
    filter(cds == dist) 


ltel.words <- glue( "The most recent number of LTEL students from https://www.cde.ca.gov/ds/ad/filesltel.asp was **{ ltel.lang$ltel.sum }**.  ") 

ltel.words2 <- if ( ltel.lang$ltel.sum >= 15 ) " Your district is required to have an LTEL dedicated action and professional development for teachers." else " Your district is NOT required to have dedicated LTEL actions."




```


`r el.words`


`r el.words2`


`r ltel.words`


`r ltel.words2`



------


## Required Metrics


<details>

<summary>[**Click here to display required metrics**]{style="color:purple;"}</summary>


```{r loop, results = "asis", echo=FALSE,  include=FALSE}

out = NULL

for(i in 1:nrow(joinder)) {
    
     out <- c(out, knit_child('child.Rmd'))
}

```


```{r output, results = "asis", echo=FALSE}
cat(paste(out, collapse = '\n'))
```


</details>


-----------

## Unduplicated Percentage 


```{r undup, echo=FALSE, include=FALSE}


undup <- undup.count %>% 
    filter(cds == dist) 

undup.words <- glue( "The most recent percentage of unduplicated students from https://www.cde.ca.gov/ds/sd/sd/filescupc.asp was **{ scales::percent( undup$undup.perc , accuracy = .1 ) }**." )


```

`r undup.words`


### Unduplicated Students' Latest Status

This section is informational only to share the current dashboard status for unduplicated student groups.  This is not required to be entered into the LCAP, however, many LEAs choose to include it in support of their contributing actions. 

<details>

<summary>[**Click here to display table**]{style="color:green;"}</summary>

```{r undups, echo=FALSE, include=TRUE, results = 'asis'}


### Unduplicated Status -----


# gt::gt(undup.mets) |>
#         tab_header(title = "Unduplicated Students' Status on Dashboard") |>
#       tab_source_note(source_note = "Source: https://www.caschooldashboard.org/" ) |>
#   cols_label(
#     long = html("Indicator"),
#     descriptive = html("Student Group"),
#     currstatus = html("2023 Status")
# 
#   )

# 
# 
DT::datatable(undup.mets,
              rownames = FALSE,
              colnames = c("Indicator","Student Group", "2023 Status" ),
              options = list(pageLength = 10)
              )



```


</details>




-----------

## Local Indicators 

As a reminder, local indicators also need to be completed on the same timeline as LCAPs.  There are three required steps. 

1. Reflect on each of the indicators using local data and evidence you have gathered.  It is highly recommended to use the self-reflection tools provided by the CDE at https://www.cde.ca.gov/ta/ac/cm/localindicators.asp
2. Present as a separate non-consent agenda item at the same governing board meeting as the LCAP is approved before the end of June. 
3. Enter the information in myCDEconnect before the deadline (TBD) and be sure to enter the date they were presented to the board in June.  



----------

This report was run at `r Sys.time()`
